---
title: "6306_CaseStudy_Unit10"
author: "Manjula Kottegoda"
date: "July 20, 2016"
output: 
  html_document:
    keep_md: true
---

## Case study

Chulwalar is part of the island group Urbano in the northern hemisphere. They 
are famous for their plants which flower in winter. There are three main plants
that Chulwalar exports:

1. Efak - a leafy bush with white flowers
2. Wuge - a grassy  plant with tiny pink flowers
3. Etel - a flowering tree (red or blue)

Exports generally are higher towards the end of the year. Chulwalar celebrates its independence on 1st December each year. On this day it
is custom to give presents to family and friends. Chulwalar also celebrates the March Equinox as a time of rebirth in the northern hemisphere.  

>In this case study we will be performing analysis and forecasting  exports for **Wuge flowers** based on the 2014 as-is, planned and influencing data. we will be analyzing  the data, running it through a variety of forecasting models and picking the best model for the case. In closing we will provide some insight on the data and export forecasting of **Wuge flowers** using the selected model.




```{r echo=FALSE, include=FALSE}
#------------------------------------------------------------------------------
#Setup Environment - Load required Packages and setwd
#------------------------------------------------------------------------------

library(fpp) # for time series forecasting and analysis
library(forecast) # for some other forecasting models
mydirectory <- 'C:/R_Git_Local/6306_CaseStudy_Unit10'
setwd(mydirectory)
```

### Data Import

First we load the 2014 data provided by the government of Chulwalar.

```{r}
#------------------------------------------------------------------------------
# Data Imports are done in this module
#------------------------------------------------------------------------------
source('Analysis/Data_Import_module.R') 
str(ImportedAsIsData)
str(ImportedPlanData)
str(ImportedIndicators)
```

Now that we have loaded the data files we can see that the file carry the foillowing values. 


Data file | Description
------------- | -----------------------------------------------------
ImportedAsIsData | observed exports data. Monthly and Annual breakdown by flower type and totals
ImportedPlanData | desired results data.Monthly and Annual breakdown by flower type and totals
ImportedIndicators | factors influencing the exports 



We will now just look at the Wuge data and it transform to a time series 
```{r}
#------------------------------------------------------------------------------
# Data seperations and transformations are done in this module
#------------------------------------------------------------------------------
source('Analysis/Data_Cleansing_module.R') 

#------------------------------------------------------------------------------
# Taking a quick look at the Raw Wuge data Data
#------------------------------------------------------------------------------
str(WugeAsIsVector) # observed exports raw data
str(WugePlanVector) # desired results raw data


#------------------------------------------------------------------------------
# Taking a quick look at the Time Series transformed data 
#------------------------------------------------------------------------------
str(WugeAsIs)  # observed exports time series data
str(WugePlan)  # desired results time series data
```



### Data exploration

#### Correlation between As Is and Plan Data for Wuge 

Correlation between *As Is* and *Plan* data is now examined to determine the accuracy of *Plan* data. Correlation is a measure of linear relationship between two variables. 

```{r}
#cor(TotalAsIs, TotalPlan )
cor(WugeAsIs, WugePlan)
#cor(YearAsIs, YearPlan)
```

As can be seen the correlation coefficient is 0.8788474 indicating a strong relationship between *As Is* & *Plan* data. In other words planning accuracy is very good.


Now we look at the statistics of the Linear fit
```{r}
WugeAsIs_lm <- lm(WugeAsIs ~ WugePlan , data = WugeAsIs)
summary(WugeAsIs_lm)
```

#### STL is now used to decompose the data into seasonal, trend and remainder components using loess.

The Wuge time series can be analysed further after seperating it trend, seasonality and remainder (remaining coincidential) components from one another.
```{r}
#------------------------------------------------------------------------------
# Use STL function for decomposition and then plot the seperated patterns
#------------------------------------------------------------------------------
WugeAsIs_stl <- stl(WugeAsIs, s.window=5)

plot(WugeAsIs_stl, col="black", main="WugeAsIs_stl")
plot(WugeAsIs_stl$time.series[,"trend"], col="blue")

```


